Variable Selection in Convex Function Estimation

### 2014-04-18 tex/scam/appendix.tex
paper update

\subsection{Proof of Additive Faithfulness}
\label{sec:faithful_proof}

We start with a proof of Lemma~\ref{lem:general_int_reduction}. We restate the lemma here for convenience.

\begin{lemma}
Let $F$ be a product distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.

Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, \E f_k(X_k) = 0\}$

Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
\end{lemma}

Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.

We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$. This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$. \\

We now turn our attention toward the $f^*_k$'s.

It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.

Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\big|^2 
                 d \mathbf{x}_{-k}.
\]
It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.

Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
  \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
      ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
     p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
              d \mathbf{x}_{-k} \\
f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
       p(\mathbf{x}_{-k}) (f(\mathbf{x}) -\mu^*) d \mathbf{x}_{-k} 
 \end{align*}
Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption. The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.

The square error objective is strongly convex. The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive. Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.

Now, we note that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.

Our reasoning actually proves something stronger. It proves the following lemma:

\begin{lemma}
\label{lem:additive_component}

$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
\[
min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
                    \,:\, \E f_k(X_k) = 0 \}
\]
for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
\end{lemma}

The next lemma adapts Lemma~\ref{lem:general_int_reduction} to convex functions.

\begin{lemma}
\label{lem:int_reduction}
Let $F$ be a product distribution on $C=[0,1]^s$ with positive density function $p$. Let $f: C \rightarrow \R$ be a convex function.

Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$

Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
\end{lemma}

\begin{proof}
The proof is identical to that of Lemma~\ref{lem:general_int_reduction}. We need only verify that $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ is convex.

This is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex. 
\end{proof}

 The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.

\begin{proposition}
\label{prop:faithful_condition}
Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.

The following are equivalent:
\begin{packed_enum}
\item $f$ does not depends on coordinate $k$
\item For all $x_k$, $\E[ f(X) | x_k] = \E f(X) $.
\end{packed_enum}
\end{proposition}

The first condition trivially implies the second.

Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = \E f(X)$.

Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
\begin{align*}
 \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
\end{align*}

For every $\mathbf{x}_{-k}$, we define the derivative
\[
g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
\]
$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.

We now describe two facts about $g$.

Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
\]

Fact 2. Because $f$ is convex, $g(\mathbf{x}_{-k})$ is a component of the subgradient $\partial_{\mathbf{x}} f(0, \mathbf{x}_{-k})$. (the subgradient coincides with the gradient by assumption that $f$ is twice differentiable)

Therefore, using the first order characterization of a convex function, we have
\begin{align*}
f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
\end{align*}

For all $x_k, \mathbf{x}_{-k}$, 
\[
f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
\]
and
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
\]
Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.

The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.

By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. (to prove this, one can first work with a 2 by 2 matrix and then use the fact that every principal submatrix of a PSD matrix must be PSD)

Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function. It follows therefore that $g = 0$ because it integrates to 0.

So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.

@@

\begin{theorem} 
The following holds regardless of whether we impose the boundedness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.

For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$.

Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:alternate_opt}. 
Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.

Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residual.

Suppose for all $j=1,...,n, k\in S^c$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.

Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}

\begin{proof}
We will omit the boundedness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.

We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.\\

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 
        + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| 
        - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}_n^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^{n-1}$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n-1$.

First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness.

Now, let us fix $k \in S^c$ and prove that $\hat{d}_k = 0, \hat{c}_k=0$ is an optimal solution.

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}_k$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

We now substitute in $d_k = \hat{d}_k = 0, c_k=\hat{c}_k=0, r_k = \hat{r}_k = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u}_k 
           - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}_k$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.

First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
\[
\lambda \mathbf{u}_k - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
\]

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n-1$.

Because we have strict inequality in the above equation, Lemma 1 from ~\cite{Wain:09a} show that all solutions must be zero on $S^c$.
\end{proof}

@@

\begin{theorem} 
Suppose assumptions A1, A2, A3 hold.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j=1,...,n,k \in S^c$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt} is zero on $S^c$.
\end{theorem}

@@

We remind the reader that $\Delta_{k,j} = \max(X_k, - X_{k(j)} \mathbf{1}_n, 0)$. Because $\hat{r}$ is empirically centered,

\begin{align*}
\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= 
              \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n) 
                                       - \frac{1}{n} \hat{r}^\tran \mathbf{1}_n X_{k(j)} \\
                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n)
\end{align*}
Our goal in this proof is to bound $\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})$ from above.

\textbf{Step 1.} We first get a high probability bound on $\| \hat{r} \|_\infty$.

\begin{align*}
\hat{r}_i &= Y_i - \bar{Y} -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- 
                      \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
	&=  f_0(X_S^{(i)}) - \bar{f_0} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) 
                   + \epsilon_i - \bar{\epsilon}
\end{align*}
Where $\bar{f_0} = \frac{1}{n} \sum_{i=1}^n f_0(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.

$\epsilon_i$ is subgaussian with subgaussian norm $\sigma$. For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$. Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.

By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.

Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.

We know that $|f_0(x)| \leq sB$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.

Then $|\bar{f_0(x)}| \leq sB$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq 3s B$.

Therefore, taking an union bound, we have that with probability at least $1-\frac{C}{n}$, 
\[
\| \hat{r} \|_\infty \leq (3 s B + c\sigma\sqrt{\log n}) 
\]

\textbf{Step 2.} We now bound $\frac{1}{n} \hat{r}^\tran \max( X, X_{k(j)} \mathbf{1})$.

\[
\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_{ki}, X_{k(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) + \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

Where $A = \{ i : ord(i) \geq j\}$ and $ord(i)$ is the order of sample $i$ where $(1)$ is the smallest element.

We will bound both terms.

\textbf{Term 1.}
\[
\trm{Want to bound} \qquad F(X_{k1},...,X_{kn}) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) 
\]

First, we note that $X_{ki}$ is bounded in the range $[-b,b]$.

We claim then that $F$ is coordinatewise-Lipschitz. Let $X_k = (X_{k1}, X_{k2},...,X_{kn})$ and $X'_k = (X'_{k1}, X_{k2}, ..., X_{kn})$ differ only on the first coordinate.

The order of coordinate $i$ in $X_k$ and $X'_k$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X_k)$ to $F(X'_k)$ and

$$ | F(X_{k1}, ..., X_{kn}) - F(X'_{k1}, ..., X'_{kn}) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$

By McDiarmid's inequality therefore, 
\[
P( | F(X_k) - \E F(X_k) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
\]

By symmetry and the fact that $\hat{r}$ is centered, $\E F(X_k) = 0$.

We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X_k)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$.

\textbf{Term 2:}

\[
\trm{Want to bound}   \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

$A$ is a random set and is probabilistically independent of $\hat{r}$.  $\mathbf{1}_A^\tran \hat{r}_A$ is the sum of a sample of $\hat{r}$ without replacement. Therefore, according to Serfling's theorem (Corollary~\ref{cor:serfling}), with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.

Since $|X_{k(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.

Now we put everything together.

Taking union bound across $p$ and $n$, we have that with probability at least $1-\delta$,

\[
| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
\]

Taking union bound and substituting in the probabilistic bound on $\|\hat{r}\|_\infty$, we get that with probability at least $1-\frac{C}{n}$,

$| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
\[
 c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn) }
\]

@@

@@

 We will use covering number and uniform convergence and will thus need to first introduce some notations. 
 \subsubsection{Notation}

>>>>

@@

\begin{theorem} 
The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.

Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\

Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\

Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
\end{enumerate}
\end{theorem}

\begin{proof} 
We will omit the Lipschitz constraint in our proof here. It is easy to add that in and check that the result of the theorem still holds.\\

We first consider the first item in the conclusion of the theorem.

We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.\\

The Lagrangian is
\begin{equation}
\label{eqn:full_lagrange}
\mathcal{L}( \{ d_k \}, \nu) = 
  \frac{1}{2n} \Big\| 
    Y - \sum_{k=1}^p  \bar{\Delta}_k d_k  \Big\|_2^2 + 
    \lambda \sum_{k=1}^p \| \bar{\Delta}_k d_k \|_\infty -
    \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki} 
\end{equation}
with the constraint that $\nu_{ki} \geq 0$ for all $k,i$.

Because $\{\hat{d}_k\}_{k \in S}$ is by definition the optimal solution of the restricted regression, it is a consequence that stationarity holds for $k \in S$, that is, $\partial_{ \{ d_k \}_{k \in S} } \mathcal{L}(d) = 0$, and that the dual variables $\nu_k$ for $k \in S$ satisfy complementary slackness.

We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$.

The Lagrangian form of the optimization, in term of just $d_k$, is
\[
\mathcal{L}(d_k, \nu_k) =
  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
  -  \bar{\Delta}_k d_k \big\|_2^2 
   + \lambda \| \bar{\Delta}_k d_k\|_\infty
  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]
with the constraint that $v_i \geq 0$ for all $i$.

The derivative of the Lagrangian is:
\begin{align*}
\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
      - \nu_k
\end{align*}
where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.

We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

\begin{align*}
\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
           - \nu_k = 0 
\end{align*}
where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$. It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ hwere the inequality is element-wise.

Let us reorder the samples so that the $i$-th sample is the $i$-smallest sample. \\

We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for some $0 < a < 1/2$. (coordinates of $\mathbf{u}$ correspond to the new sample ordering) We then just need to show that
\begin{align*}
- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
   \textrm{for each } j \\
- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
   + \lambda (X_{kn} - X_{kj})a &\geq 0 
\end{align*}
where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that:

\begin{align*}
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0
\end{align*}

The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way.

The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is:
\[
\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki}
\]

The exact same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.

@@

\begin{theorem} 
Suppose assumptions A1-A4 hold.

Suppose $\lambda_n \geq \mathbf{c} s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
\]

And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\ref{opt:alternate_opt_concave} are zero. 
\end{theorem}

@@

Fix $j$ and $i$. $\hat{r}^\tran \mathbf{1}_{(i':n)}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$. We will then use Serfling's theorem on the concentration of measure of sampling without replacement. (corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.\\

\textbf{Step 1}: Bounding $\| \hat{r} \|_\infty$.

$\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where $\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex additive function outputted by the restricted regression.

Both $f_0(x_i)$ and $\hat{f}(x_i)$ are coordinate-wise $L$-Lipschitz and therefore are bounded by $2 sLb$.

Because $w_i$ is subgaussian, $|w_i| \leq \mathbf{c} \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$. By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.

We now put this together and take another union bound across all $j$ and all $i'$:
\begin{align*}
\| \hat{r} \|_\infty &\leq \mathbf{c} (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
      &\leq \mathbf{c} sLb \sigma \sqrt{\log \frac{2}{\delta}}
\end{align*}
with probability at least $1 - n^2 p \delta$. We supposed that both $sLb \geq 2$ and $\sigma\sqrt{\log \frac{2}{\delta}} \geq 2$.

\textbf{Step 2}: Bounding $| \frac{1}{n} \hat{r}^\tran \mathbf{1} |$.

\begin{align*}
\frac{1}{n} \hat{r}^\tran \mathbf{1} &= 
    \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i - \hat{f}(x_i) \\
  &= \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i \quad \trm{ ($\hat{f}$ is centered)}
\end{align*}

Because $|f_0(x_i)| \leq sLb$, the first term $| \frac{1}{n} \sum_{i=1}^n f_0(x_i)|$ is at most $2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$ by Hoeffding Inequality.

Because $w_i$ is subgaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $2 \sigma \sqrt{ \frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.

Taking an union bound, we have that

\begin{align*}
| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
with probability at least $1-2\delta$.\\

\textbf{Step 3}: We now apply Serfling's theorem.

Serfling's theorem states that with probability at least $1 - \delta$:
\[
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)}\Big| \leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
\]

Taking an union bound across previous events, we have that with probability at least $1 - 3n^2 p \delta$, for all $j \in S^c$, for all $i'=1,...,n$:
\begin{align*}
\Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
  \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
Setting $\delta = \frac{1}{n^3 p}$ gives the desired result.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 We first introduce notations.
 \subsubsection{Notation} 
\label{sec:false_negative_proof_notations}
